### 2019-01-26 Sections/economics_of_the_quantum_internet.tex
+cooperative enh

The utility payoff enhancement characterised by the transformation given in Eqs.~(\ref{eq:util_payoff_enh_1} \& \ref{eq:util_payoff_enh_2}) is the simplest of toy models where unification is assumed to be perfectly efficient -- there no overheads associated with unification, nor are there any externalities, such as taxes or regulations. However, such secondary effects can easily be incorporated into the model by modulating Eq.~(\ref{eq:util_payoff_enh_2}) with additional layers of transformations capturing these features. For example, consider the unification of computational resources between two players residing in different jurisdictions, which levy import/export tariffs\index{Tariffs} against one another, an externality introducing inefficiency into cooperative strategies. When expressed in terms of the monetary cost of computation, this would effectively modulate the payoffs of \textsc{Unify} matrix elements by a tariff-dependent function.

>>>>

The utility payoff enhancement characterised by these transformations is based on the simplest of toy models where unification is assumed to be perfectly efficient -- there no overheads (e.g transaction or communication costs) associated with cooperation, nor are there any externalities, such as taxes or regulations. However, such secondary effects can easily be incorporated into the model by modulating them with additional layers of transformations capturing these features. For example, consider the unification of computational resources between two players residing in different jurisdictions, which levy import/export tariffs\index{Tariffs} against one another, an externality introducing inefficiency into cooperative strategies. When expressed in terms of the monetary cost of computation, this would effectively modulate the payoffs of \textsc{Unify} matrix elements by a tariff-dependent function.
